Rotating Stars from \Kepler Observed with Gaia DR2

### 2018-04-30 paper/ms.tex
outlining things

@@

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/B_V_rot}
\caption{
}
%\label{fig:cmd}
\end{figure}

>>>>

data xmatched by M. Bedell between Kepler DR25 (CITE) and Gaia DR2 (CITE), using 1arcsec radius.
distances using the updated prescription from \citet{bailer-jones2018}

@@

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/B_V_rot}
\caption{converted to B-V using Padova isochrone colors. 3 gyrochrones from \citet{meibom2009} with ages 300 Myr (dark red), 600 Myr (bright red), and 1.2 Gyr (blue) are shown.
}
%\label{fig:cmd}
\end{figure}
